---
title: "Practice Upload"
author: "Zjrobbin"
date: "6/14/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Making the Map

##### [Landownership](https://www.fs.usda.gov/rds/archive/Product/RDS-2017-0007)

Citation: 

Hewes, Jaketon H.; Butler, Brett J.; Liknes, Greg C. 2017. Forest ownership in the conterminous United States circa 2014: distribution of seven ownership types - geospatial dataset. Fort Collins, CO: Forest Service Research Data Archive. https://doi.org/10.2737/RDS-2017-0007

Description: 

From the FS Website

This data publication contains 250 meter raster data depicting the
spatial distribution of forest ownership types in the conterminous
United States. The data are a modeled representation of forest land by
ownership type, and include three types of public ownership: federal,
state, and local; three types of private: family (includes individuals
and families), corporate, and other private (includes conservation and
natural resource organizations, and unincorporated partnerships and
associations); as well as Native American tribal lands. The most
up-to-date data available were used in creating this data publication.

A plurality of the ownership data were from 2014, but some data were as
old as 2004.


```{r cars}
library(raster)
Own<-raster("C:/Users/zacha/Desktop/Harvest_Validator/Ownership_Resampled.tif")
plot(Own)
```

#### Normalizing by day and area 

```{r pressure}
Own[Own$Ownership_Resampled,]<-Own[Own$Ownership_Resampled,]*365/10000
plot(Own)
```

