---
title: "SCRAPPLE_maps_05282020"
author: "kj"
date: "5/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#set to root model folder
wd<-"C:\\Users\\zacha\\Desktop\\CNRM-CM5rcp85\\"

library(raster)
library(rgeos)
library(viridisLite)
library(spatialEco)
library(RColorBrewer)
library(rasterVis)
library(ggplot2)
library(dplyr)
```

## Annual Fire Weather Index 

```{r}
Climate<-read.csv(paste0(wd,"Climate-future-input-log.csv"))
YearlyFWI<-Climate %>%
            group_by(Year)%>%
            summarise_at(vars(FWI),list(mean=mean,max=max))

plot(seq(0,93),YearlyFWI$mean,type="l",col=magma(10),ylim=c(0,70),lwd=3.0,xlab="Time",ylab="FWI",main="Fire Weather Index")
lines(seq(0,93),YearlyFWI$max,col="red",lwd=3.0)
legend(0,70,legend=c("Mean FWI","Max FWI"),lty=c(1,1),lwd=c(3,3),col=c("black","red"))

```

## Days above 30 FWI 

```{r,fig.width=10.0,fig.height=10.0}
Climate$one<-1
Climatetrun<-Climate[Climate$FWI>30,]
YearlyFWICount<-Climatetrun %>%
            group_by(Year)%>%
            summarise_at(vars(one),list(sum=sum,max))
plot(YearlyFWICount$Year,YearlyFWICount$sum,ylab="Days above FWI 30",type="l",col="red",lwd=3.0,
     main="Days above FWI 30 For The Landscape")                        
                         
```

## Total Landscape Statistics

```{r,fig.width=10.0,fig.height=10.0}
Scrrple_Sum=read.csv(paste0(wd,"scrapple-summary-log.csv"))
plot(Scrrple_Sum$TotalBurnedSitesAccidental,type="l",ylim=c(0,5000),lwd=3.0,
     xlab="Time",ylab="Sites Burned",col="blue",main="Sites Burned by Type")
lines(Scrrple_Sum$TotalBurnedSitesLightning,type="l",lwd=3.0,
     col="green")
lines(Scrrple_Sum$TotalBurnedSitesRx,type="l",lwd=3.0,
     col="orange")
legend(0,5000,legend=c("Accidental","Rx","Ligthning"),lty=c(1,1),
       lwd=c(3,3),col=c("blue","orange","green"))



```


```{r,fig.width=10.0,fig.height=10.0}
plot(Scrrple_Sum$NumberFiresAccidental,type="l",ylim=c(0,5000),lwd=3.0,
     xlab="Time",ylab="Ignitions Burned",col="blue",main="Ignitions burned by type")
lines(Scrrple_Sum$NumberFiresLightning,type="l",lwd=3.0,
     col="green")
lines(Scrrple_Sum$NumberFiresRx,type="l",lwd=3.0,
     col="orange")
legend(0,5000,legend=c("Accidental","Rx","Ligthning"),lty=c(1,1),
       lwd=c(3,3),col=c("blue","orange","green"))

```

## Comparison between historical and simulated ignition.

```{r,fig.width=10.0,fig.height=10.0}
FiresInAppsH<-read.csv(paste0(wd,"FiresInAppsHuman2.csv"))
FiresInAppsH$Ones<-1
#colnames(FiresInAppsH)
FiresbyyearH<-FiresInAppsH %>%
                group_by(FIRE_YEAR)%>%
              summarise_at(vars(Ones),list(sum=sum))
FiresInAppsL<-read.csv(paste0(wd,"FiresInAppsLightning2.csv"))
FiresInAppsL$Ones<-1
#colnames(FiresInAppsL)
FiresbyyearL<-FiresInAppsL %>%
                group_by(FIRE_YEAR)%>%
              summarise_at(vars(Ones),list(sum=sum))
data<-data.frame(name=c(rep("Simulation Accidental",length(Scrrple_Sum$NumberFiresAccidental)),
                        rep("Historical Accidental",length(FiresbyyearH$sum)),
                        rep("Simulation Lightening",length(Scrrple_Sum$NumberFiresLightning)),
                        rep("Historical Lightening",length(FiresbyyearL$sum))),
                 value=c(Scrrple_Sum$NumberFiresAccidental,FiresbyyearH$sum,
                         Scrrple_Sum$NumberFiresLightning,FiresbyyearL$sum))
#boxplot(Scrrple_Sum$NumberFiresAccidental,Firesbyyear$sum,names=c("Simulation","Historical"))
Vio<-ggplot(data,aes(x=name,y=value,fill=name))+
  geom_violin()+
  stat_summary(fun=mean, geom="point", shape=23, size=2,col="black")+
  scale_fill_brewer(palette="Dark2")+
  scale_x_discrete(limits=c("Simulation Accidental", "Historical Accidental", 
                              "Simulation Lightening","Historical Lightening"))
  
Vio
```


## Severity Landscape


```{r,fig.width=10.0,fig.height=10.0}
plot(Scrrple_Sum$NumberCellsSeverity1,type="l",ylim=c(0,5000),lwd=3.0,
     xlab="Time",ylab="Ignitions Burned",col="grey")
lines(Scrrple_Sum$NumberCellsSeverity2,type="l",lwd=3.0,
     col="orange")
lines(Scrrple_Sum$NumberCellsSeverity3,type="l",lwd=3.0,
     col="red")
legend(0,5000,legend=c("Low Severity","Mid Severity","High Severity"),lty=c(1,1),
       lwd=c(3,3),col=c("grey","orange","red"))
```



## How many times did a cell burn in the simulation? Equivalent average return interval?

Similar to burn frequency figure in Scrapple manuscript

```{r,fig.width=10.0,fig.height=10.0}

#bring this in so it can be used to resample the landis outputs
sapp_ecoregion<-raster(paste0(wd,"11_Ecoregions.tif"))


#get all of the yearly day of fire rasters
year_rasts<-list.files(paste0(wd,"scrapple-fire\\"),pattern="day-of-fire")

#create empty stack
rastperyear<-stack()

#for all the rasters that are read in turn to raster, add to stack
for (raster in 1:length(year_rasts)){
  
year<-raster(paste0(wd,"scrapple-fire\\",year_rasts[raster]))
rastperyear <-stack(rastperyear,year)
  
}

#make reclassification matrix to get when if burned
m <- c(0, 1, 0,  2, 365, 1)
rclmat <- matrix(m, ncol=3, byrow=TRUE)
rc <- raster::reclassify(rastperyear, rclmat)

#sum all of the 1's in a cell to get years burned acros landscape
years_burned<-sum(rc)

#do all the necessary things to landis outputs to get them computable
extent(years_burned)<-extent(sapp_ecoregion)
projection(years_burned)<-"+proj=utm +zone=17 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0" 
years_burned_newres<- resample(years_burned,sapp_ecoregion,method = 'ngb')

plot(years_burned_newres,col=magma(10),main="Number of Years Burned")

# Average Reccurrence Interval (1/Burn Freq)
avg_ret_inter<-100/years_burned_newres
#par(mar=c(1.0,1.0,1.0,1.0))
plot(avg_ret_inter,col=viridis(10),colNA="black",main="Average Return Interval",axes=F,box=F)
```


## Did a given cell burn? 

BInary implification of above

```{r,fig.width=10.0,fig.height=10.0}
#so when we go to do our reclass burn area, we'll say 0 to 1 is actually  0
#reclass burn frequency to just did it burn, or did it not burn? 
m2 <- c(0, .5, 0,  1, 6, 1)
rclmat2 <- matrix(m2, ncol=3, byrow=TRUE)
burn_y_n<- raster::reclassify(years_burned, rclmat2)
names(burn_y_n)<-"burns_y_n"

plot(burn_y_n,col=magma(2),legend=FALSE,main="Cells that burned",axes=F,box=F)
```


## Spread probability 

0's (ie where no fires occurred in a given year) are removed. Average, Max, Min, and Range of Spread probability for a cell are mapped. 

```{r,fig.width=10.0,fig.height=10.0}

#get all of the yearly day of fire rasters
year_spread_rasts<-list.files(paste0(wd,"scrapple-fire"),pattern="fire-spread-probability")

yearly_spreadprob<-stack()


#this doesn't not put them in temporal order because of file naming, would need to correct if shooting for time series plots
for (raster in 1:length(year_spread_rasts)){

year<-raster(paste0(wd,"scrapple-fire\\",year_spread_rasts[raster]))
year[year == 0] <- NA
yearly_spreadprob <-stack(yearly_spreadprob,year)

}

avg_spreadprob<-mean(yearly_spreadprob,na.rm=TRUE)
max_spreadprob<-max(yearly_spreadprob,na.rm=TRUE)
min_spreadprob<-min(yearly_spreadprob,na.rm=TRUE)

extent(avg_spreadprob)<-extent(sapp_ecoregion)
extent(max_spreadprob)<-extent(sapp_ecoregion)
extent(min_spreadprob)<-extent(sapp_ecoregion)

projection(avg_spreadprob)<-"+proj=utm +zone=17 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"
projection(max_spreadprob)<-"+proj=utm +zone=17 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"
projection(min_spreadprob)<-"+proj=utm +zone=17 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"


avgspread_newres<- raster::resample(avg_spreadprob,sapp_ecoregion,method = 'ngb')
minspread_newres<- raster::resample(min_spreadprob,sapp_ecoregion,method = 'ngb')
maxspread_newres<- raster::resample(max_spreadprob,sapp_ecoregion,method = 'ngb')

dif_max_min<-maxspread_newres-minspread_newres

plot(avgspread_newres,col=viridis(15), colNA="black",main="Average Fire Spread Probability",axes=F,box=F)
plot(maxspread_newres,col=viridis(15), colNA="black",main="Max Fire Spread Probability",axes=F,box=F)
plot(minspread_newres,col=viridis(15), colNA="black",main="Min Fire Spread Probability",axes=F,box=F)
plot(dif_max_min,col=viridis(15), colNA="black",main="Does a cell exhibit the same spread probability throughout the simulation (maximum-minimum)?",axes=F,box=F)

```

## Fire Intensity 

-Min/Max fire intensity across the landscape
-How many max intens fires occur? 

```{r}
# #average intensity
# 
# year_int_rasts<-list.files(paste0(wd,"scrapple-fire"),pattern="fire-intensity")
# 
# yearly_intens_rast<-stack()
# yearly_max_intens<-stack()
# 
# for (raster in 1:length(year_int_rasts)){
# 
# 
# year1[]
# year1<-year
# year1[year1!=3]<-NA
# 
# 
# }
# yearly_intens_rast<-stack(paste0(wd,"scrapple-fire","\\",year_int_rasts))
# yearly_max_intens<-yearly_intens_rast[yearly_intens_rast!=3]<-NA
# 
# #max intens
# max_intens<-max(yearly_intens_rast,na.rm=TRUE)
# 
# #maximum intensity as factor, gettin ready for plotting
#   max_intens<-as.factor(max_intens)
#   rat <- levels(max_intens)[[1]]
#   rat[["intensity"]] <- c("nofire","intens 1","intens2", "intens3")
#   levels(max_intens) <- rat
#   num_levels<-nrow(levels(max_intens)[[1]])
# 
# ## Plot
# rasterVis::levelplot(max_intens, col.regions=rev(terrain.colors(num_levels)), xlab="", ylab="",main="Maximum Intensity Observed")
#   
# 
# #count how many maximum intensity fires
# sum_maxintens<-sum(yearly_max_intens,na.rm=TRUE)/3
# 
# plot(sum_maxintens,col=magma(6),main="Number of High Intensity (3) Fires")

```


## Percent of specific polygons that burned

Not necessarily telling for the model, but a start if trying to extract/analyze specific management areas

- There are 8 ownership classes shown here, but I believe there are only supposed to be 7 accoridng to the original dataset. May want to check creation/structure of "Ownership_Resampled.tif"?

```{r}

#not sure why there are 8 classes?
#read in zjr ownership
sapp_own<-raster(paste0(wd,"Ownership_Resampled.tif"))

# #maximum intensity as factor, gettin ready for plotting
#   sapp_own<-as.factor(sapp_own)
#   rat <- levels(sapp_own)[[1]]
#   rat[["ownership"]] <- c("federal","state","local", "family","corporate","other-private","tribal","unknown?")
#   levels(sapp_own) <- rat
#   num_levels<-nrow(levels(sapp_own)[[1]])
# 
# ## Plot
# rasterVis::levelplot(sapp_own, col.regions=rev(terrain.colors(num_levels)), xlab="", ylab="",main="Ownership Type")
#      

#creating percent formula to pass to zonal.stats
pct_burned <- function(x, p=1, na.rm = FALSE) {
  if ( length(x[x == p]) < 1 ) return(0)
  if ( length(x[x == p]) == length(x) ) return(1)
  else return( length(x[x == p]) / length(x) )
}

#percentage of AOIs burned
extent(sapp_own)<-extent(burn_y_n)
projection(burn_y_n)<-"+proj=utm +zone=17 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0" 
burn_y_n_newres<- raster::resample(burn_y_n,sapp_own,method = 'ngb')

#break stats up by sub-AOI
stats_test_own<-as.data.frame(zonal(burn_y_n_newres, sapp_own,fun='pct_burned', digits=0, na.rm=TRUE))

stats_test_own$owner<-c("federal","state","local", "family","corporate","other-private","tribal","unknown?")
print(stats_test_own)

```



```{r}
### Mean fire return interval

# #percentage of AOIs burned
# extent(sapp_own)<-extent(avg_ret_inter)
# projection(burn_y_n)<-"+proj=utm +zone=17 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0" 
# avg_ret_inter_res<- raster::resample(avg_ret_inter,sapp_own,method = 'ngb')
# avg_ret_inter_res[avg_ret_inter_res==Inf]<-NA
# unique(avg_ret_inter_res)
# #break stats up by sub-AOI
# stats_test_own<-as.data.frame(zonal(avg_ret_inter_res, sapp_own,fun=mean, digits=0, na.rm=TRUE))
# 
# stats_test_own$owner<-c("federal","state","local", "family","corporate","other-private","tribal","unknown?")
# print(stats_test_own)


#avg_ret_inter
```



## Looking at suppression effectiveness

```{r}
sapp_Suppress<-raster(paste0(wd,"Suppressionmap2.tif"))
extent(sapp_own)<-extent(avg_spreadprob)
projection(avg_spreadprob)<-"+proj=utm +zone=17 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0" 
avg_spreadprob_res<- raster::resample(avg_spreadprob,sapp_Suppress,method = 'ngb')
avg_spreadprob_res[avg_spreadprob_res==0]<-NA
#unique(avg_spreadprob)
#break stats up by sub-AOI
stats_test_supress<-as.data.frame(zonal(avg_spreadprob_res, sapp_Suppress,fun=mean, digits=0, na.rm=TRUE))

stats_test_supress$Supression<-c("No Supression","One","Two","Three")
print(stats_test_supress)

```




```{r,fig.width=10.0,fig.height=10.0}
#display.brewer.all()
Heat=brewer.pal(9,'YlOrRd')
Heatramp<-colorRampPalette(Heat)
Heatramp<-Heatramp(100)


Ignition_type<-stack(paste0(wd,"scrapple-fire/",
                     list.files(paste0(wd,"scrapple-fire/"),
                                pattern="ignition-type-")))
#### Accidental Ignition 2 
Ignition2<-Ignition_type
Ignition2[Ignition2 != 2]<-0
SumofAccidental<-sum(Ignition2)
plot(SumofAccidental,col=Heatramp,
     zlim=c(1,10),axes=F,box=F,main="Number of Accidental Fires")
SumofAccidental[SumofAccidental==0]<-.01
#plot(100/SumofAccidental,col=Heatramp,zlim=c(0,200))

#### Ignition Lightning 3 
Ignition3<-Ignition_type
Ignition3[Ignition3 != 3]<-0
SumofOne<-sum(Ignition3)
plot(SumofOne,col=Heatramp,zlim=c(1,10),axes=F,box=F,main="Number of Lightening Fires")

#### Ignition RX 4 
Ignition3<-Ignition_type
Ignition3[Ignition3 != 4]<-0
SumofOne<-sum(Ignition3,col=Heatramp)
plot(SumofOne,col=Heatramp,zlim=c(1,40),axes=F,box=F,main="Number of Rx Fires")

```

